---
title: "Ret"
author: "Nd"
date: '2022-06-02'
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

## Intro to markdown

Markdown allows you to do things like **bold** *italic* and more!

Make a list wit asterisks like: \* bold with double-asterisk \* italics
with underscores \* code-type fond with backticks

You can also use hyphens instead of asterisks.

For a number list: 1. bold.... 1. italic.... 1. code....


Hyperlinks are like [Hyperlinked text] (https://mylink.org)

```{r load data}
gap <- gapminder

```


```{r make-plot}
plot(lifeExp ~ year, data=gap)
```



view(gap)
view(gap)
```{r}
temp  <- c(1,2,3)
```
```{r}

```



```{r make cats}
cats <- data.frame(coat = c("calico", "black", "tabby"),
                  weight=c(2.1, 5.0, 3.2),
                  likes_string = c(1, 0, 1))
write.csv(x = cats, file = "data/feline-data.csv",
          row.names= FALSE)
```

```{r read_cats2}
read.csv('data/feline-data.csv')
```



Creating Vectors and coercing types

```{r}
my_vector <- vector(mode='character',length=3)
combine_vector <- c(1,2,"bananas")
```

change names

```{r}
names(cats)[3] <- "likes_hunting"
```

Add comumns and rows to data frames
```{r}
cats <- read.csv('data/feline-data.csv')
age <- c(2,3,5)
cats <- cbind(cats, age)
newRow <- list("tortoiseshell", 3,3,TRUE, 9)
cats <- rbind(cats,newRow)
```


Create a vector called human_age by multiplying cats$age by 7
```{r}
human_age <- 7 * cats$age
```

Convert human_age to factor
```{r}
human_age <- as.factor(human_age)
```

convert to numeric and divide by 7
```{r}
human_age <- as.numeric(as.character(human_age))
```

Divide by 7
```{r}
 human_age/7
```
remove rows and columns
```{r}
cats$coats <- as.factor(cats$coat)
cats <- rbind(cats,c("white,3,4,0,1"))
#remove a row
cats <- cats[-5,]
#cats <- na.omit(cats)
cats[,-4]

drop <- names(cats) %in% c("weight")
cats[,!drop]
```

